Quantum H theorem, variational entropy, and relaxation processes

### 2021-01-06 tex/quantum.tex
Typos: sec. 3

Arguing that the energy exchange between particles is dominated by collisions between particles,
and using perturbation theory, the rate of change in the number of particles in a group $\kappa$ is
%
\begin{eqnarray}\label{eq:changen}
    \frac{d n_{\kappa}}{dt}&=&-\sum_{\lambda,(\mu \nu)}A_{\kappa\lambda,\mu\nu} n_{\kappa}n_{\lambda}(g_{\mu}\pm n_{\mu})(g_{\nu}\pm n_{\nu})\nonumber \\
    &&+\sum_{\lambda,(\mu \nu)}A_{\mu\nu,\kappa\lambda} n_{\mu}n_{\nu}(g_{\kappa}\pm n_{\kappa})(g_{\lambda}\pm n_{\lambda}).
\end{eqnarray}
%
Here $A_{\kappa\lambda,\mu\nu}n_{\kappa}n_{\lambda}(g_{\mu}\pm n_{\mu})(g_{\nu}\pm n_{\nu})$ is the
expected number of collisions per unit time, in which two particles will be moved from groups
$\kappa$, $\lambda$ to $\mu$, $\nu$, and the tensor $A_{\kappa\lambda,\mu\nu}n_{\kappa}$ is given by
%
\begin{equation}\label{eq:amnkldef}
  A_{\kappa\lambda,\mu\nu}=\frac{4\pi^{2}}{h}\frac{|I_1\pm I_2|^2}{\Delta \epsilon}.
\end{equation}
%
In Eq.~(\ref{eq:amnkldef}), $\Delta\epsilon$ is the net energy change occuring during the
collision and $|I_1-I_2|^2=|V_{mn,kl}|^2$ where
$V_{mn,kl}$ is the element of the transition matrix of a binary collision.
It is important to remark that in deriving Eq.~(\ref{eq:changen}), the equal a priori
probabilities and the random a priori phases hypotheses were surmised, and that 
the random a priori phases hypothesis can be
considered an analogous to the molecular chaos hypothesis
\cite{bib:das2018}.

>>>>

Arguing that the energy exchange between particles is dominated by collisions between particles,
and using perturbation theory, the rate of change in the number of particles in a group $\kappa$ is
%
\begin{eqnarray}\label{eq:changen}
    \frac{d n_{\kappa}}{dt}&=&-\sum_{\lambda,(\mu \nu)}A_{\kappa\lambda,\mu\nu} n_{\kappa}n_{\lambda}(g_{\mu}\pm n_{\mu})(g_{\nu}\pm n_{\nu})\nonumber \\
    &&+\sum_{\lambda,(\mu \nu)}A_{\mu\nu,\kappa\lambda} n_{\mu}n_{\nu}(g_{\kappa}\pm n_{\kappa})(g_{\lambda}\pm n_{\lambda}).
\end{eqnarray}
%
Here $A_{\kappa\lambda,\mu\nu}n_{\kappa}n_{\lambda}(g_{\mu}\pm n_{\mu})(g_{\nu}\pm n_{\nu})$ is the
expected number of collisions per unit time, in which two particles will be moved from groups
($\kappa$, $\lambda$) to ($\mu$, $\nu$), and the tensor $A_{\kappa\lambda,\mu\nu}$ is given by
%
\begin{equation}\label{eq:amnkldef}
  A_{\kappa\lambda,\mu\nu}=\frac{4\pi^{2}}{h}\frac{|I_1\pm I_2|^2}{\Delta \epsilon}.
\end{equation}
%
In Eq.~(\ref{eq:amnkldef}), $\Delta\epsilon$ is the net energy change occuring during the
collision and $|I_1-I_2|^2=|V_{mn,kl}|^2$ where
$V_{mn,kl}$ is the element of the transition matrix of a binary collision.
It is important to remark that in deriving Eq.~(\ref{eq:changen}), the equal a priori
probabilities and the random a priori phases hypotheses were surmised, and that 
the random a priori phases hypothesis can be
considered an analogous to the molecular chaos hypothesis
\cite{bib:das2018}.
